Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
reflow

<!-- intro -->
<!-- QW: could focus on just talking about the importance of scale for behavioural and spatial ecology. Why is it important and what are the more broadly applicable ideas that lead us to this paper -->
Animal social systems are characterized and influenced by three types of scale. 
Social scale defines the type and measurement of social relationships and directly
impacts observed sociality between individuals. Spatial scale, in this study,
reflects the resolution of the habitat within which social interactions occur. 
Finally, temporal scale is related to both study design and network robustness
as well as seasonal differences in resources, patch dynamics or
landscape connectivity. By parsing social systems into discrete contexts 
using multilayer networks, we highlight the influence of social, spatial and temporal scales
on animal social systems, demonstrating the importance of considering biologically
relevant and robust observational scales. 
<!-- intro -->

>>>>

<!-- intro -->
Animal social systems are characterized and influenced by three types of scale.
Social scale defines the type and measurement of social relationships and
directly impacts observed sociality between individuals. Spatial scale, in this
study, reflects the resolution of the habitat within which social interactions
occur. Finally, temporal scale is related to both study design and network
robustness as well as seasonal differences in resources, patch dynamics or
landscape connectivity. By parsing social systems into discrete contexts using
multilayer networks, we highlight the influence of social, spatial and temporal
scales on animal social systems, demonstrating the importance of considering
biologically relevant and robust observational scales.
<!-- intro -->
